---
title: "cytoinstaller"
author: "mike"
date: "11/15/2020"
output:
  github_document:
always_allow_html: true
---


This package is a lightweight wrapper of some functions in [`remotes`](https://github.com/r-lib/remotes).
It installs the most recent version of cyto packages from the common public repositories e.g. Bioconductor, CRAN,  as well as `CYTO` repository, which provides the cyto packages built by github actions triggered by pushed commits. 

## Installation

Install the released version of remotes from CRAN:

```r
remotes::install_github("RGLab/cytoinstaller")
```

## Usage

To install the latest version of a cyto package (and also install or update its dependencies.)

```r
cytoinstaller::install_cyto("ggcyto")
```

To get the package info from `CYTO` repo,

```r
cytoinstaller::cyto_repo("ggcyto")
```

To list all the package info,

```r
cytoinstaller::cyto_repo()
```



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}
library(cytoinstaller)
library(kableExtra)
library(dplyr)
cyto_repos <- getOption("cyto_repos")
df <- do.call(rbind, lapply(cyto_repos, function(pkg){
                            data.frame(package = pkg
                                       , release = paste0("https://github.com/RGLab/", pkg, "/workflows/build/badge.svg?branch=release")
                                       , devel = paste0("https://github.com/RGLab/", pkg, "/workflows/build/badge.svg?branch=master")
                                       , link = paste0("https://github.com/RGLab/", pkg, "/actions") 
                                      )
                          })
            )
df1 <- df
```

## CYTO repo build status

```{r, echo=FALSE}
df[,1:3] %>% mutate(release := "", devel := "") %>% 
  kbl(booktabs = T) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, link = df1$link)%>%
  column_spec(2, image = df1$release)%>%
  column_spec(3, image = df1$devel)
```

